### 2017-04-06 paper/evaluation.tex
quick pass on RQ5

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      question~\ref{questionThree}.}
\end{wrapfigure}
The goal of the first two questions is to identify potential
discrepancies between the environment used to obtain our results and
environment of the developers.  Overall, we found that \Fix{...}

\Mar{... estou aqui ...}

Based on the answers from the developers, we confirmed that most of
the subjects execution time was compatible with the results found at
Section~\ref{sec:rqA}. From Question I, we noticed that \emailsCI{}
developers confirmed the use of an continuous integration server to
run tests, which \emailsDistributed{} of them is using a distributed
continuous integration server as an alternative to parallelism.
From a local development, \emailsLocal{} developers answered that they
run tests in a local machine, and \emailsNotDescribed{} developers did
not described their environment.
From Question II, we noticed that \emailsSequential{} confirmed that
they do not execute tests in parallel, and \emailsParallel{} did not
confirmed, however, the developers confirmed the need of an extra
parameter at the command line to execute in parallel.
From Question III, \emailsA{} of developers do not know that
parallelism is an available configuration for Maven Surefire,
\emailsB{} of developers do not use parallel testing concerned with
concurrency issues, \emailsD{} of developers uses a continuous
integretion server for run tests while working \Luis{here I want to
say that they use it for something like "non-blocking testing" while
developing in a local machine}, \emailsD{} of developers thinks that
it is not worthy the effort, and \emailsNA{} of developers did not
answered the last question, or did not knew an answer.

>>>>

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      question~\ref{questionThree}.}
\end{wrapfigure}
The goal of the first two questions is to identify potential
discrepancies between the environment used to obtain our results and
the environment of developers.  Overall, we found that \Fix{...}

\Mar{... estou trabalhando neste texto ...}

Based on the answers from developers, we confirmed that most of the
subjects execution time was compatible with the results found at
Section~\ref{sec:rqA}.

\Fix{revise...} From Question I, we noticed that \emailsCI{}
developers confirmed the use of an continuous integration server to
run tests, which \emailsDistributed{} of them is using a distributed
continuous integration server as an alternative to parallelism.
From a local development, \emailsLocal{} developers answered that they
run tests in a local machine, and \emailsNotDescribed{} developers did
not described their environment.

Considering question 2, we found that \emailsSequential{} of the
\emailsProjectsAnswered{} projects indeed did not execute tests in
parallel.  The discrepancy is justified by cases where neither of our
checks (static or dynamic) could detect presence of parallelism.  \Fix{elaborate}

%% did not confirmed, however,
%% the developers confirmed the need of an extra parameter at the command
%% line to execute in parallel.

From Question III, \emailsA{} of developers do not know that
parallelism is an available configuration for Maven Surefire,
\emailsB{} of developers do not use parallel testing concerned with
concurrency issues, \emailsD{} of developers uses a continuous
integretion server for run tests while working \Luis{here I want to
say that they use it for something like "non-blocking testing" while
developing in a local machine}, \emailsD{} of developers thinks that
it is not worthy the effort, and \emailsNA{} of developers did not
answered the last question, or did not knew an answer.
